Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-09-11 SupportingInformation.Rmd
modified

source("FittingCopula_selective_loc.R")  # top most hierarchy source file
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_aphid_count<-RES_single_sp(d_allsp=data_aphid_count,sp=10,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_count,paste(resloc,file="AphidCopulaFit_selecloc_count_species_10.RDS",sep=""))
```

@@

source("FittingCopula_selective_loc.R")  # top most hierarchy source file
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n"))
RES_aphid_ff<-RES_single_sp(d_allsp=data_aphid_ff,sp=11,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n")) 
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_ff,paste(resloc,file="AphidCopulaFit_selecloc_firstflight_species_11.RDS",sep=""))
```

@@

set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_plankton_north_sea<-RES_single_sp(d_allsp=data_plankton_north_sea,sp=16,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=45)
#cat(paste("stop-time: ",Sys.time(),"\n"))    
resloc<-"./Results/fitting_results/"
saveRDS(RES_plankton_north_sea,paste(resloc,file="Plankton_North_Sea_CopulaFit_selecloc_species_16.RDS",sep=""))
```

@@

set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_methane<-RES_single_sp(d_allsp=methane_data,sp=1,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=50)
#cat(paste("stop-time: ",Sys.time(),"\n"))    
resloc<-"./Results/fitting_results/"
saveRDS(RES_methane,paste(resloc,file="MethaneFluxFit_selecloc_data_pt_thrs_50.RDS",sep=""))
```

>>>>

source("FittingCopula_selective_loc.R")  # top most hierarchy source file
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_aphid_count<-RES_single_sp(d_allsp=data_aphid_count,sp=10,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30,
                               good_loc_given=F,good_loc=NA)
#cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_count,paste(resloc,file="AphidCopulaFit_selecloc_count_species_10.RDS",sep=""))
```

@@

source("FittingCopula_selective_loc.R")  # top most hierarchy source file
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n"))
RES_aphid_ff<-RES_single_sp(d_allsp=data_aphid_ff,sp=11,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30,
                            good_loc_given=F,good_loc=NA)
#cat(paste("stop-time: ",Sys.time(),"\n")) 
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_ff,paste(resloc,file="AphidCopulaFit_selecloc_firstflight_species_11.RDS",sep=""))
```

@@

set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_plankton_north_sea<-RES_single_sp(d_allsp=data_plankton_north_sea,sp=16,families=c(1,3:10,13,14,16:20),level=0.05,
                                      data_pt_thrs=45,good_loc_given=F,good_loc=NA)
#cat(paste("stop-time: ",Sys.time(),"\n"))    
resloc<-"./Results/fitting_results/"
saveRDS(RES_plankton_north_sea,paste(resloc,file="Plankton_North_Sea_CopulaFit_selecloc_species_16.RDS",sep=""))
```

@@

set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_methane<-RES_single_sp(d_allsp=methane_data,sp=1,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=50,
                           good_loc_given=F,good_loc=NA)
#cat(paste("stop-time: ",Sys.time(),"\n"))    
resloc<-"./Results/fitting_results/"
saveRDS(RES_methane,paste(resloc,file="MethaneFluxFit_selecloc_data_pt_thrs_50.RDS",sep=""))
```
